---
output: html_document
params:
  phu_id: "3895"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
confirmed_cases_file <- "~/RProjects/COVID/confirmed_cases.csv"
confirmed_cases <- read.csv(confirmed_cases_file)
covid_status_by_PHU_file <- "~/RProjects/COVID/covid_status_by_PHU.csv"
covid_status_by_PHU <- read.csv(covid_status_by_PHU_file)
phu_name <- str_to_title(covid_status_by_PHU$PHU_NAME[covid_status_by_PHU$PHU_NUM == params$phu_id][1])
library(plotly)
library(tidyverse)
```

# `r covid_status_by_PHU$PHU_NAME[covid_status_by_PHU$PHU_NUM == params$phu_id][1]`

This is the latest information on file for `r phu_name`

## Overall trend

This next section is supposed to show an interactive graph charting the case count for `r phu_name` against the province of Ontario.  They will be plotted against independent y axes so trends can be more easily compared
```{r plot_case_count}
phu_df <- covid_status_by_PHU[covid_status_by_PHU$PHU_NUM == params$phu_id,] %>% arrange(FILE_DATE)
province_data <- covid_status_by_PHU %>% group_by(FILE_DATE) %>% summarize(ACTIVE_CASES = sum(ACTIVE_CASES), RESOLVED_CASES = sum(RESOLVED_CASES), DEATHS = sum(DEATHS))
province_data$PHU_NAME <- "ONTARIO"
province_data$PHU_NUM <- 0
#phu_df <- phu_df %>% union(province_data)
phu_plot <- plot_ly(
  phu_df,
  x = ~FILE_DATE,
  y = ~ACTIVE_CASES,
  name = ~PHU_NAME,
  type = 'scatter',
  mode = 'lines'
) %>% add_trace(
  data = province_data,
  x = ~FILE_DATE,
  y = ~ACTIVE_CASES,
  type = 'scatter',
  mode = 'lines',
  yaxis = "y2"
) %>% layout(
  yaxis2 = list(overlaying = "y", side = "right")
)
phu_plot
```


## Trend by age group

The below chart shows the same data as above, but broken down by age group.  It is interesting to see where each group falls over time.
```{r trend_by_age_group}
# This gives me a table showing how many new cases were reported by date, PHU, and age group
cases_by_age <- confirmed_cases %>% group_by(Case_Reported_Date, Reporting_PHU_ID, Age_Group) %>% summarize(n = n()) %>% pivot_wider(names_from = Age_Group, values_from = n)
cases_by_age[is.na(cases_by_age)] <- 0
cases_by_age$Case_Reported_Date <- as.Date(cases_by_age$Case_Reported_Date)

# Next we apply a 14 day rolling sum, as my current understanding is that cases are considered "Active" for 14 days from being reported

active_cases_by_age <- RcppRoll::roll_sum(cases_by_age$`50s`[cases_by_age$Reporting_PHU_ID == '3895'], align = 'left')

rollingsum <- function(df, phu) {
  data <- df[df$Reporting_PHU_ID == phu,]
  rolling_data <- as_tibble(RcppRoll::roll_sum(as.matrix(data[,-(1:2)]), align = 'right', fill=0,na.rm=FALSE, n=14)) 
  return(data.frame(data[,1:2],rolling_data))
}

tester <- rollingsum(cases_by_age,params$phu_id)

phu_plot <- plot_ly(
  tester,
  x = ~Case_Reported_Date,
  y = ~X90.,
  name = "90+",
  type = 'scatter',
  mode = 'lines'
) %>% add_trace(
  y = ~X80s,
  name = "80s",
  type = 'scatter',
  mode = 'lines'
) %>% add_trace(
  y = ~X70s,
  name = "70s",
  type = 'scatter',
  mode = 'lines'
) %>% add_trace(
  y = ~X60s,
  name = "60s",
  type = 'scatter',
  mode = 'lines'
) %>% add_trace(
  y = ~X50s,
  name = "50s",
  type = 'scatter',
  mode = 'lines'
) %>% add_trace(
  y = ~X40s,
  name = "40s",
  type = 'scatter',
  mode = 'lines'
) %>% add_trace(
  y = ~X30s,
  name = "30s",
  type = 'scatter',
  mode = 'lines'
) %>% add_trace(
  y = ~X20s,
  name = "20s",
  type = 'scatter',
  mode = 'lines'
) %>% add_trace(
  y = ~X.20,
  name = "<20",
  type = 'scatter',
  mode = 'lines'
) %>% add_trace(
  y = ~UNKNOWN,
  name = "Unknown",
  type = 'scatter',
  mode = 'lines'
) %>% layout(title = "Active case count by age group",
             xaxis = list(title="Date"),
             yaxis = list(title="# of Active Cases"))

phu_plot
```

## Trend by age group and population

```{r age_group_and_population}
# Get population by age group and PHU

# Divide positive by age group and PHU

# Use same plot from above
print("More to come here soon...")
```